Power Estimation for VTR

### 2012-12-10 doc/power/power_manual.tex
Power: Added callibration
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/trunk@1305 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Update to power manual
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/trunk@1335 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

@@

\newpage
\section{Overview}
	TBD (\autoref{fig:flow}).
\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.8]{images/flow.pdf}
	\caption{Power Estimation in the VTR Flow}
	\label{fig:flow}
\end{figure}

\newpage
\section{Running VTR with Power Estimation}
\subsection{VTR Flow}
\subsection{VTR Tasks}
\subsection{VPR 6.0}
The following command-line options are added to the VPR executable to facilitate power estimation (all are required): \newline
\texttt{\--\--power}:  Use this option to enable power estimation. \newline
\texttt{\--\--activity\_file <activities.act>}: The activity file, produce by ACE 2.0, or another tool. \newline
\texttt{\--\--tech\_properties <tech\_properties.xml>}: The technology properties XML file.

\newpage
\section{Supporting Tools}
\subsection{Technology Properties Generation}
Power estimation requires information detailing the properties of the CMOS technology.  
This information, which includes transistor capacitances, leakage currents, etc. is included in an \texttt{.xml} file, and provided as a parameter to VPR.
This XML file is generated using a script which automatically runs HSPICE, performs multiple circuit simulations, and extract the necessary values.

@@

\subsection{ACE 2.0 Activity Estimation}
Power estimation requires activity information for the entire netlist.  This ativity information consists of two values:
\vspace{-10pt}
\begin{enumerate}
	\item  \underline{The Signal Probability}, $P_1$, is the long-term probability that a signal is logic-high.  For example, a clock signal with a 50\% duty cycle will have $P_1(clk) = 0.5$.
	\item \underline{The Transition Density} (or switching activity), $A_S$, is the average number of times the signal will switch during each clock cycle.  For example, a clock has $A_S(clk)=2$.
\end{enumerate}

@@

\newpage
\section{Architecture Modelling}
The following section describes the architectural assumptions made by the power model, and the related parameters in the architecture file.

@@

\textbf{NOTE:} Default Leakage Mode TBD

@@

@@

\clearpage
\section{Other Architecture Options \& Techniques}
\subsection{Area Estimations} \label{sec:area_est}
The power estimator performs area estimations of both the global routing structures and the complex blocks.  The CLB area is determined through a recursive function that counts the area of interconnect, buffers, and primitives (flip-flops and LUTs).

@@

\subsection{SRAM}
TBD

>>>>

The latest version of this document can be obtained here: \url{http://vtr-verilog-to-routing.googlecode.com/svn/trunk/doc/power/power_manual.pdf}

@@

\newpage
\section{Overview}
This document describes the power estimation tool for VTR.  This tool provides transistor-level dynamic and static power estimates for a given architecture and circuit.

\autoref{fig:flow} illustrates how the VTR flow is modified to add power estimation.  The actual power estimation is performed within the VPR executable; however, additional files must be provided.  In addition to the circuit and architecture files, power estimation requires files detailing the signal activities and technology properties.

\autoref{sec:running} details how to run power estimation for VTR.  \autoref{sec:tools} provides details on the supporting tools that are used to generate the signal activities and technology properties files.  \autoref{sec:arch_modelling} provides details about how the tool models architectures, including different options of modelling methods.  \autoref{sec:options} provides more advanced configuration options.

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.8]{images/flow.pdf}
	\caption{Power Estimation in the VTR Flow}
	\label{fig:flow}
\end{figure}

\newpage
\section{Running VTR with Power Estimation} \label{sec:running}
\subsection{VTR Flow}
	The easiest way to run the VTR flow is to use the \texttt{run\_vtr\_flow.pl} script.  See \url{http://code.google.com/p/vtr-verilog-to-routing/wiki/Run_VTR_Flow} for instructions on how to use the script.

In order to perform power estimation, you must add the following options:

\begin{BVerbatim}[bgcolor=LightGray, boxwidth=\textwidth]
-power 
-cmos_tech <cmos_technology_properties_file.xml>
\end{BVerbatim}

The CMOS technology properties file is an XML file that contains relevant process-dependent information needed for power estimation. XML files for 22\,nm, 45\,nm, and 130\,nm PTM models can be found here:

\begin{BVerbatim}[bgcolor=LightGray, boxwidth=\textwidth]
<vtr>/vtr_flow/tech/.../*.xml
\end{BVerbatim}

See \autoref{sec:tpg} for information on how to generate an XML file for your own SPICE technology model.

%\subsection{VTR Tasks}
\subsection{VPR 6.0}
The easiest way to perform power estimation is to use the \texttt{run\_vtr\_flow.pl} script.  However, if you wish, you may run VPR directly.
The following command-line options are added to the VPR executable to facilitate power estimation (all are required): \newline
\texttt{\--\--power}:  Use this option to enable power estimation. \newline
\texttt{\--\--activity\_file <activities.act>}: The activity file, produce by ACE 2.0, or another tool. \newline
\texttt{\--\--tech\_properties <tech\_properties.xml>}: The technology properties XML file.

This requires a activity file, which can be generated as described in \autoref{sec:ace}.

\newpage
\section{Supporting Tools} \label{sec:tools}
\subsection{Technology Properties Generation} \label{sec:tpg}
Power estimation requires information detailing the properties of the CMOS technology.  
This information, which includes transistor capacitances, leakage currents, etc. is included in an \texttt{.xml} file, and provided as a parameter to VPR.
This XML file is generated using a script which automatically runs HSPICE, performs multiple circuit simulations, and extract the necessary values.

@@

\subsection{ACE 2.0 Activity Estimation} \label{sec:ace}
Power estimation requires activity information for the entire netlist.  This ativity information consists of two values:
\vspace{-10pt}
\begin{enumerate}
	\item  \underline{The Signal Probability}, $P_1$, is the long-term probability that a signal is logic-high.  For example, a clock signal with a 50\% duty cycle will have $P_1(clk) = 0.5$.
	\item \underline{The Transition Density} (or switching activity), $A_S$, is the average number of times the signal will switch during each clock cycle.  For example, a clock has $A_S(clk)=2$.
\end{enumerate}

@@

\newpage
\section{Architecture Modelling} \label{sec:arch_modelling}
The following section describes the architectural assumptions made by the power model, and the related parameters in the architecture file.

@@

%\textbf{NOTE:} Default Leakage Mode TBD

@@

It is assumed that the power usage specified here includes power of all child \texttt{pb\_types}.  No further recursive power estimation will be performed.

@@

\clearpage
\section{Other Architecture Options \& Techniques} \label{sec:options}
\subsection{Area Estimations} \label{sec:area_est}
The power estimator performs area estimations of both the global routing structures and the complex blocks.  The CLB area is determined through a recursive function that counts the area of interconnect, buffers, and primitives (flip-flops and LUTs).

@@

%\subsection{SRAM}
%TBD
